#Linear Regression Report 
<br />
*`r input$name`* <br />   
*`r as.character(format(Sys.Date(), format="%B %d, %Y"))`*

<br />

This report was created using the `r input$datasetame` data set.  The dependent variable in my analysis is `r input$outcome` and independent numeric variables in my analysis are `r input$varnum` and independent categorical variales are `r input$varcat`. 

###1. Scatterplots

<br />

The scatterplot of `r input$outcome` and `r input$varnum` appear below. 

```{r,echo=FALSE}
if (length(input$varnum)==1){
  plot(as.formula(paste(input$outcome,"~",input$varnum)),data=Dataset(),xlab=input$varnum,ylab=input$outcome,main=paste("Scatterplot for",input$outcome,"versus",input$varnum))
}else if (length(input$varnum)>1){
  pairs(as.formula(paste("~",paste(c(input$varnum,input$outcome),collapse="+"))),data=Dataset())
}
```

`r input$text_scatt` 

<br />

###2. Boxplot

<br />

The boxplot of `r input$outcome` and `r input$varnum` appear below. 

```{r,echo=FALSE}
if (length(input$varcat)==1){
      par(mfrow=c(1,1))
      boxplot(as.formula(paste(input$outcome,"~",input$varcat)),xlab=input$varcat,ylab=input$outcome,data=Dataset(),main=paste("Boxplot of",input$outcome,"versus",input$varcat))
    }else if (length(input$varcat)==2){
      par(mfrow=c(1,2))
      for (i in 1:length(input$varcat)){
        boxplot(as.formula(paste(input$outcome,"~",(input$varcat)[i])),xlab=(input$varcat)[i],ylab=input$outcome,data=Dataset(),main=paste("Boxplot of",input$outcome,"versus",(input$varcat)[i]))
      }
    }else if (length(input$varcat)==3 || length(input$varcat)==4){
      par(mfrow=c(2,2))
      for (i in 1:length(input$varcat)){
        boxplot(as.formula(paste(input$outcome,"~",(input$varcat)[i])),xlab=(input$varcat)[i],ylab=input$outcome,data=Dataset(),main=paste("Boxplot of",input$outcome,"versus",(input$varcat)[i]))
      }
    }else if (length(input$varcat)==5 ||length(input$varcat)==6){
      par(mfrow=c(2,3))
      for (i in 1:length(input$varcat)){
        boxplot(as.formula(paste(input$outcome,"~",(input$varcat)[i])),xlab=(input$varcat)[i],ylab=input$outcome,data=Dataset(),main=paste("Boxplot of",input$outcome,"versus",(input$varcat)[i]))
      }
    }else if (length(input$varcat)==7 ||length(input$varcat)==8 ||length(input$varcat)==9){
      par(mfrow=c(3,3))
      for (i in 1:length(input$varcat)){
        boxplot(as.formula(paste(input$outcome,"~",(input$varcat)[i])),xlab=(input$varcat)[i],ylab=input$outcome,data=Dataset(),main=paste("Boxplot of",input$outcome,"versus",(input$varcat)[i]))
      }
    }
```

`r input$text_box` 

<br />

###3. Summary Statistics

<br />

The summary statistics appear below. 

```{r,echo=FALSE}
summary(model())

```

`r input$text_summary` 

<br />

###4. Diagnostic plots

<br />

The diagnostic plots for model appear below. 

```{r,echo=FALSE}
par(mfrow=c(2,2))
    plot(model())
```

`r input$text_diagno` 

<br />

###5. Added Variable Plots

<br />

The added variable plots appear below. 

```{r,echo=FALSE}
if ((dim(summary(model())$coef)[1]-1)<=9){
      avPlots(model())
    }else avPlots(model(),ask=FALSE,layout=c(5,3))
```

`r input$text_added` 

<br />

###6. Marginal model plots

<br />

The marginal model plots appear below. 

```{r,echo=FALSE}
if (is.null(input$varnum)&&is.null(input$varcat)==FALSE) {
  return(NULL)
  }else if(is.null(input$varnum)==FALSE){
mmps(model(),terms=as.formula(paste("~",paste(input$varnum,collapse="+"))))
  }
```

`r input$text_mmp` 

<br />

